Chapter 2 Figures

### 2019-12-30 doc/figureFiles/figures.Rmd
working on figure for Bret, started vert figure

@@

@@

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Number of Crossovers per Cell")+
  geom_point(aes(shape = sex), size=3, position=position_dodge(.5))+

@@

```{r Strain.fig.merge.v2, echo=FALSE}
Fig1_Bv2_strain
#save a tif or png file
ggsave("~./MLH1repo/doc/figureFiles/MLH1Fig1.png")
```

>>>>

# Option vertical facets

@@

```{r vertical.facet, echo=FALSE, fig.height= 13}

Vert.facet <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Number of Crossovers per Cell")+
  geom_point(aes(shape = sex), size=3, position=position_dodge(.5))+

   facet_wrap(~sex, ncol = 1)+ #, scales = "free", space="free"

  ylim(c(17.5, 33))+
 scale_color_manual(values=colors_of_strains)+ 
  scale_y_continuous(breaks=seq(20,32,2) )+

#remove y labfor male 
  #Dom
  annotate("segment", x=.75, xend=3.6, y=21, yend=21, colour="black", size=1)+

  #Musc
  annotate("segment", x=3.9, xend=6.15, y=21, yend=21, colour="black", size=1)+
  #mol
  annotate("segment", x=6.5, xend=8.1, y=21, yend=21, colour="black", size=1)

   #label -- segments applied to both facets, labels not?
#label annotation not working, add in illustrator  
annotate("text", x = c(2.2, 4.5, 7,
                         2.2, 4.5, 7), #list of all x points 
           y = c(20.2,20.2,20.2,
                 20.2,20.2,20.2),
   label = c("M. m. domesticus","M. m. musculus", "M. m. molossinus",
             "M. m. domesticus","M. m. musculus", "M. m. molossinus"),
           fontface = 'italic', hjust = 0.5, size=3.5)

  Vert.facet

```{r new.save, echo=FALSE}
#Fig1_Bv2_strain
#save a tif or png file
#ggsave("~./MLH1repo/doc/figureFiles/MLH1Fig1.png")
```

First run of the vertica facets looks awful and squished. fix it.

@@

Fig1_Bv2_strain <- ggplot(strain.table.HQ, aes(y=mean_co, x=strain, color=strain, shape = sex))+
  #facet_grid(~sex, scales = "free", space="free")+ 
  ylab("Number of Crossovers per Cell")+
  geom_point(aes(shape = sex), size=3.7, position=position_dodge(.5))+

@@

```{r Strain.fig.merge.v2, echo=FALSE}
Fig1_Bv2_strain
#save a tif or png file
#ggsave("~./MLH1repo/doc/figureFiles/MLH1Fig1.png")
```
